\bf An Unitary RG-based Auxiliary Model Approach\\ to Strongly-Correlated Systems

### 2023-03-08 notes/notes.tex
added correlation functions

\section{Single-particle Green's function}

@@

>>>>

\section{Mapping greens functions from the bulk to the auxiliary model}

@@

A particular example of this relation between the Greens functions is the following: static correlation functions of the form \(\braket{\Psi_\text{gs} | \mathcal{O}_1^\dagger \mathcal{O}_2 | \Psi_\text{gs}}\) can be written in terms of auxiliary model correlations:
\begin{equation}\begin{aligned}
	\braket{\Psi_\text{gs} | \mathcal{O}_1^\dagger(\vec R_0) \mathcal{O}_2(\vec R_0) | \Psi_\text{gs}} \simeq \frac{1}{\lambda_{\vec k_0}^2}\braket{\psi_\text{aux}(\vec R_0, \vec a) | \mathcal{O}_1^\dagger(d) \mathcal{O}_2(d) | \psi_\text{aux}(\vec R_0, \vec a)}\\
	\braket{\Psi_\text{gs} | \mathcal{O}_1^\dagger(\vec R_0 + \vec a) \mathcal{O}_2(\vec R_0) | \Psi_\text{gs}} \simeq \frac{1}{\lambda_{\vec k_0}^2 \mathcal{W}}\braket{\psi_\text{aux}(\vec R_0, \vec a) | \mathcal{O}_1^\dagger(z) \mathcal{O}_2(d) | \psi_\text{aux}(\vec R_0, \vec a)}~,
\end{aligned}\end{equation}
where \(\mathcal{O}_{1,2}\) are operators that describe the correlation we are computing, and the arguments \((d)\) and \((z)\) indicate that the corresponding operator acts at the impurity site and the bath zeroth site respectively.
